---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(dplyr)
```
# eddington

<!-- badges: start -->
[![CRAN\_version](http://www.r-pkg.org/badges/version/eddington)](https://cran.r-project.org/package=eddington)
[![Number\_of\_Downloads](https://cranlogs.r-pkg.org/badges/grand-total/eddington)](https://cran.r-project.org/package=eddington)
[![Travis-CI Build Status](https://travis-ci.org/pegeler/eddington2.svg?branch=master)](https://travis-ci.org/pegeler/eddington2)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/pegeler/eddington2?branch=master&svg=true)](https://ci.appveyor.com/project/pegeler/eddington2)
<!-- badges: end -->

One statistic that cyclists are known to track is their Eddington number. The
Eddington number for cycling, _E_, is the maximum number where a cyclist has
ridden _E_ miles on _E_ distinct days. So to get a number of 30, you need to
have ridden 30 miles or more on 30 separate days.

This package provides functions to compute a cyclist's Eddington number,
including efficiently computing cumulative _E_ over a vector. These functions
may also be used for _h_-indices for authors. Both are specific applications of
computing the side length of a Durfee square.

## Installation

You can install the released version of eddington from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("eddington")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("pegeler/eddington2/R/package")
```

## Example

Here is a basic example showing how to get the summary Eddington number of the
included **simulated** `rides` dataset. Note that we first have to aggregate
ride mileage by date.

```{r example}
library(eddington)
library(dplyr)

rides %>%
  group_by(ride_date) %>%
  summarize(n = n(), total = sum(ride_length)) %>% 
  summarize(E = E_num(total)) %>% 
  pull
```

See the package vignette for detailed usage. 
